DATA 621 Week #1 Textbook Exercises

### 2019-09-07 DATA621/Week 01 Textbook Exercises.Rmd
Minor change

---
title: "DATA 621 Week #1 Textbook Exercises"
author: "Mike Silva"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

>>>>

---
title: "DATA 621 Week #1 Textbook Exercises"
author: "Mike Silva"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    code_folding: "hide"
---
